---
title: "Exploring FARS data"
author: "Tony Sellu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

This package allows you to easily analyze data from the US National Highway
Traffic Safety Administration's Fatality Analysis Reporting System, which is a
nationwide census providing the American public yearly data regarding fatal
injuries suffered in motor vehicle traffic crashes.

The specific functions in this package (see below) are designed to be used in
reading and analyzing data from the Fatality Analysis Reporting System, which
is a nationwide census providing the American public yearly data regarding fatal
injuries suffered in motor vehicle traffic crashes.
[More details](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars)

Make sure that you have downloaded FARS data before running the functions below.
The data files should be at the root of your working directory.

```{r}
library(dplyr)
library(readr)
library(maps)
library(week4pkg)
```

## make_filename(<year>)

Create filenames that look like accident_<year>.csv.bz2

```{r eval=FALSE}
make_filename(2015)
```

## fars_read(<filename>)

Creates a dataframe from the filename specified.

```{r eval=FALSE}
fars_read("accident_2015.csv.bz2")
```

## fars_read_years()

Creates a dataframe for the years specified.

```{r eval=FALSE}
fars_read_years(2013:2015)
```

## fars_summarize_years()

Summarizes the data for the years specified.

```{r eval=FALSE}
fars_summarize_years(2013:2015)
```

## fars_map_state()

Map locations of accidents
```{r eval=FALSE}
fars_map_state('05', 2015)
```
